A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-18 doc/sigchi14/conclusion.tex

\section{Conclusion and Future Work}
Our prototype does not yet have a general way of communicating device descriptions and capabilities - this means our prototype cannot yet control new, unknown devices - they first have to be modeled. We may extend the PUC work~\cite{nichols} to address this issue.

More importantly though, the main limitation is that extra hardware for IR communication is needed for the HMD and each controllable device. One potential approach would be to combine the growing availability of high-resolution indoor maps with live data from the HMD's camera to determine what a user is looking at without IR data exchange.

\bjoern{add some general summary}

>>>>

\section{Conclusion}
We introduced a novel method for selecting and controlling smart appliances in physical spaces through  infrared targeting based on head orientation. While we present a prototype approach that requires that the user carry additional hardware, all parts can readily be miniaturized and integrated into future head-worn hardware. We also introduced a disambiguation technique in case head orientation is not sufficient to determine a unique target. We characterized our devices performance, arguing that it is matched well to the amount of head movement people can control without strain. A target acquisition study showed that the technique is efficient; a home control scenario showed promise but also limitations when trying to control complex appliances. As our environment continues to be populated by a swarm of sensing and actuation devices, methods to interrogate and control our smart environments may become increasingly important.
%\section{Acknowledgments}
%We thank our user study participants and the a
